\documentclass{article}
\usepackage[british]{babel}
\usepackage{ragged2e}
\usepackage{enumitem}
\usepackage[singlespacing]{setspace}   % other options: [singlespacing], [onejalfspacing] or [doublespacing]
\usepackage[a4paper,margin=1in]{geometry}

% Lengths
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
% Formatting
\newlist{deepenum}{enumerate}{6}
\setlist[deepenum,1]{label=\arabic*.,  parsep=\baselineskip, leftmargin=2em, labelwidth=*, align=left}
\setlist[deepenum,2]{label*=\arabic*., parsep=\baselineskip, leftmargin=3em, labelwidth=*, align=left}
\setlist[deepenum,3]{label*=\arabic*., parsep=\baselineskip, labelwidth=*, align=left} % leftmargin=3em
\setlist[deepenum,4]{label*=\arabic*., parsep=\baselineskip, labelwidth=*, align=left} % leftmargin=4em
\setlist[deepenum,5]{label*=\arabic*., parsep=\baselineskip, labelwidth=*, align=left} % leftmargin=5em
\setlist[deepenum,6]{label*=\arabic*., parsep=\baselineskip, labelwidth=*, align=left} % leftmargin=3em

% Macros
\NewDocumentCommand\lawtitle{O{\baselineskip} O{\baselineskip} m}{%
    \begingroup
        \vspace{#1}
        \centering \textbf{#3}\par
        \vspace{#2}
    \endgroup}

\begin{document} \sffamily

Dear Someone,

\lawtitle[1cm][1cm]{Re: Topic of the letter goes here}

\begin{deepenum}
    \item Every paragraph has to be numbered. I do this with a set of Word style. Every paragraph has to be numbered. I do this with a set of Word style.
    \item And so one.
    \begin{deepenum}
        \item Here are sub-paragraphs. They are numbered, too.
        \item As you can see.
        \begin{deepenum}
            \item Six levels of numbering.
            \begin{deepenum}
                \item Another level.
                \begin{deepenum}
                    \item And another level.
                    \begin{deepenum}
                        \item The last level.
                    \end{deepenum}
                \end{deepenum}
            \end{deepenum}
        \end{deepenum}
    \end{deepenum}
    {\bfseries \item Only the sicth levels could be a heading. In which case it's bold}
    \item[] Sometimes the next level under doesn't have a para number (because it's only subparagraph). Sometimes the next level under doesn't have a para number (because it's only subparagraph)
    \item[] Sometimes else.
    \item Another regular paragraph.
\end{deepenum}

\bigskip

And we'll sign off with para with no number


\vspace{\fill}  % Moves everything to the bottom
\begin{singlespace}
    \RaggedRight%
    Yours faithfully,\par
    \textbf{Erza Legal}\par
    \bigskip    
    Per:\par
    (Signature gets inserted here)\par
    \bigskip
    \textbf{John Smith},\par
    Solicitor\par
    Email:my@email.address.com
\end{singlespace}
\end{document}